Correctly Optimizing Abstract Abstract Machines

### 2013-03-29 paper/paper.tex
Drop mem from front page.

\begin{figure}[t]
\small
\begin{center}
\includegraphics[width=3.2in]{church-relative-space}
\includegraphics[width=3.2in]{church-relative-speed}
\includegraphics[width=3.2in]{church-relative-time}
\vspace{-1.5em}
\end{center}
\caption{Factor improvements over the baseline analyzer for the
  \Church{} benchmark in terms of peak memory usage, the rate of state
  transitions, and total analysis time. (Bigger is better.) Each point
  is marked with the section that introduces the optimization.}
\label{fig:churchtime}
\end{figure}

@@

We evaluated the precision of these techniques with a singleton
variable analysis to find opportunities to inline constants and closed
functions. We found no change in the results across all
implementations, including Shivers' timestamp approximation.

>>>>

\begin{figure}[t]
\small
\begin{center}
%\includegraphics[width=3.2in]{church-relative-space}
\includegraphics[width=3.2in]{church-relative-speed}
\includegraphics[width=3.2in]{church-relative-time}
\vspace{-1.5em}
\end{center}
\caption{Factor improvements over the baseline analyzer for the
  \Church{} benchmark in terms of the rate of state
  transitions and total analysis time. (Bigger is better.) Each point
  is marked with the section that introduces the optimization.}
\label{fig:churchtime}
\end{figure}

@@

To determine the impact of these techniques on precision, we evaluated
the a singleton variable analysis to find opportunities to inline
constants and closed functions.  We found no change in the results
across all implementations, including Shivers' timestamp
approximation---from an empirical point of view, these techniques are
precision preserving despite the theoterical loss of precision.
